Transfer learning for \'echelle spectroscopy with \texttt{blas\'e}

### 2022-03-03 paper/paper1/ms.tex
Woohoo, we made 4 figures today

\section{Refining the model from data with transfer learning}
\begin{outline}
    \1 Augment the pre-trained model with extrinsic parameters:
    \2 vsini and RV
    \1 How to re-sample into the data space?
    \1 Option 1: Convolve the Pseudo-Voigt with a Instrumental Gaussian
    \2 The convolution of a Gaussian with a Pseudo-Voigt is simply a new Pseudo-Voigt!
    \2 Simply evaluate on a new coarse wavelength grid! Saves computation!
    \1 Option 2: Numerically convolve output on a fine grid and sum pixels
    \2 Computationally wasteful
    \2 Requires generating full bandwidth spectrum at native resolution
    \1 Both options should give the same answer (right?)
    \2 Need to double-check commutativity of convolution and element-wise product...
    \1 Ideally you need wavelength-dependent resolution, not just a single stock resolving power
    \1 Need accurate per-pixel uncertainties
    \1 We have to apply some amount of regularization to the pre-trained model
    \2 Regularization tunes how much to trust the data versus the model in the semi-empirical model
    \2 No Regularization means likely to overfit noise in the data
    \2 Too much regularization resembles a static (fixed) PHOENIX model
\end{outline}

>>>>

\section{Refining the model from data with transfer learning}

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/blase_WASP69_demo.png}
    \caption{WASP 69 observed with HPF, compared to a $T_{\mathrm{eff}}=4700\;$K,  $\log{g}=4.5$ solar metallicity PHOENIX model warped to $v\sin{i}=2.2$~km/s, $RV=-9.6$~km/s, and HPF resolving power.}
    \label{fig_WASP69_demo}
\end{figure}

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/blase_WASP69_transfer_learned.png}
    \caption{Semi-empirical model of WASP 69 transfer-learned with \texttt{blas\'e}. }
    \label{fig_WASP69_transferred}
\end{figure}

\begin{outline}
    \1 Augment the pre-trained model with extrinsic parameters:
    \2 vsini and RV
    \1 How to re-sample into the data space?
    \1 Option 1: Convolve the Pseudo-Voigt with a Instrumental Gaussian
    \2 The convolution of a Gaussian with a Pseudo-Voigt is simply a new Pseudo-Voigt!
    \2 Simply evaluate on a new coarse wavelength grid! Saves computation!
    \1 Option 2: Numerically convolve output on a fine grid and sum pixels
    \2 Computationally wasteful
    \2 Requires generating full bandwidth spectrum at native resolution
    \1 Both options should give the same answer (right?)
    \2 Need to double-check commutativity of convolution and element-wise product...
    \1 Ideally you need wavelength-dependent resolution, not just a single stock resolving power
    \1 Need accurate per-pixel uncertainties
    \1 We have to apply some amount of regularization to the pre-trained model
    \2 Regularization tunes how much to trust the data versus the model in the semi-empirical model
    \2 No Regularization means likely to overfit noise in the data
    \2 Too much regularization resembles a static (fixed) PHOENIX model
\end{outline}
